Black hole symphony orchestra: Spectroscopy using gravitational wave signals from the inspiral, merger and ringdown of binary black holes

### 2020-11-26 papers/intro_paper/intro_paper.tex
updated figures and notebooks for the paper

@@

\appendix
\section{Study of noise syetematics on ringdown measurements}\label{sec:noise_systematics}

@@

In order to investigate the

>>>>

\section*{ACKNOWLEDGEMENTS}\label{sec:acknowledgements}
LIGO Clusters

@@

\appendix
\section{Study of syetematics on ringdown measurements}\label{sec:noise_systematics}

@@

In Section~\ref{sec:method}, we mentioned that the expression of the Bayesian likelihood function outlined in Eqs.~\ref{eq:likelihood} and \ref{eq:nwip} is only valid if the interferometric noise can be described as a stationary Gaussian process. LIGO-Virgo noise, however, frequently has non-stationary and/or non-Gaussian features, like glitches, PSD drift, etc, which can affect parameter inferences unless appropriately accounted for.

Here we demonstrate with an example, systematic biases likely originating from an incomplete understanding of the noise using the example of the GW190521. In Fig.~\ref{ig:o1o2_events} \abhi{include GW190521A in figure}, we find the estimates of the fractional deviations in the damping time, $\dtau{220}$ does not enclose the GR prediction at the 90 \% credible level, although the fractional deviation in the frequency $\df{220}$ is.
